An Invariant Framework for Conducting Reproducible Computational Science

### 2015-01-15 evaluation.tex
Minor changes

The re-execution time is half or less than half of the original execution time in both cases. During the original execution, the input dataset is either locally available or comes from HDFS, which is accessed through FUSE. During the package creation procedure, all the input dataset has been copied from HDFS into the package on the local filesystem. So, the re-execution procedure can get its input from the local filesystem instead of obtaining the input dataset from HDFS.

Both packages created by Parrot and PTU are a subset of the root filesystem, which only includes all the accessed files. The original relationship, such as symbolic links, between files and directories is maintained. The files from pseudo filesystems such as proc and dev, are ignored. The re-execution procedure uses these pseudo filesystems from the host machine through redirection techniques.
The sizes of the packages created by Parrot and PTU are nearly the same, 18GB. 
Except for the accessed files, both Parrot and PTU preserve the execution environment of the application. 
the PTU package also includes a leveldb-format provenance information of the application with the size of 3 MB.

>>>>

The re-execution time is half or less than half of the original execution time in both cases of the \emph{TauRoast} application. During the original execution, the input dataset is either locally available or comes from HDFS, which is accessed through FUSE. During the package creation procedure, all the input dataset has been copied from HDFS into the package on the local filesystem. So, the re-execution procedure can get its input from the local filesystem instead of obtaining the input dataset from HDFS.

Both packages created by Parrot and PTU are a subset of the root filesystem, which only includes all the accessed files. The original relationship, such as symbolic links, between files and directories is maintained. The files from pseudo filesystems such as proc and dev, are ignored. The re-execution procedure uses these pseudo filesystems from the host machine through redirection techniques.
For the \emph{TauRoast} application, the sizes of the packages created by Parrot and PTU are nearly the same, 18GB. 
Except for the accessed files, both Parrot and PTU preserve the execution environment of the application. 
the PTU package also includes a leveldb-format provenance information of the application with the size of 3 MB.

### 2015-01-15 observation.tex
Minor changes

\item {\bf Identifying all dependencies.}  Due to the distributed nature of HEP applications, the applications typically depend on a large number of external and local dependencies.
External dependencies are often explicitly stated, such as when the application makes connections to Github resources, and CVS servers for downloading source. 
However, when the application has distributed execution then implicit network connections are present requiring us to identify dependencies on all machines where execution takes place. 
Implicit local dependencies arise due to mounted filesystems. In TauRoast, the application data and code is distributed on five networked filesystems, and in Athena on two networked filesystems. 
Since these filesystems appear local to the application machine, it is important to check and capture mounted filesystems and their respective mount points.

@@

\item {\bf Dependencies for Reproducible Execution.} Capturing the necessary and sufficient dependencies that are part of an application is sufficient for repeatability, but possibly for not reproducibility, 
Repeatability implies if a result depends on running program X, we must be able to run exactly X again. In reproducibility the goal is rarely limited to running
\emph{precisely} what a predecessor did. Often, the objective is to
change a parameter or a data input in order to see how the result is affected. To that end, the preservation system must capture enough of the surrounding
material to permit modifications to succeed. In Athena framework, for instance, the software library needed to include basic software programs such as make, awk, sed that can aid further development.  
Further, a better understanding of how end users will consume preserved software will help to shape how
software is preserved in the first place.
\end{itemize}

>>>>

\item {\bf Identifying all dependencies.}  Due to the distributed nature of HEP applications, the applications typically depend on a large number of external and local dependencies.
External dependencies are often explicitly stated, such as when the application makes connections to Github resources, and CVS servers for downloading source. 
However, when the application has distributed execution then implicit network connections are present requiring us to identify dependencies on all machines where execution takes place. 
Implicit local dependencies arise due to mounted filesystems. In \emph{TauRoast}, the application data and code is distributed on five networked filesystems, and in \emph{Athena} on two networked filesystems. 
Since these filesystems appear local to the application machine, it is important to check and capture mounted filesystems and their respective mount points.

@@

\item {\bf Dependencies for Reproducible Execution.} Capturing the necessary and sufficient dependencies that are part of an application is sufficient for repeatability, but possibly for not reproducibility.
Repeatability implies if a result depends on running program X, we must be able to run exactly X again. In reproducibility the goal is rarely limited to running
\emph{precisely} what a predecessor did. Often, the objective is to
change a parameter or a data input in order to see how the result is affected. To that end, the preservation system must capture enough of the surrounding
material to permit modifications to succeed. In Athena framework, for instance, the software library needed to include basic software programs such as make, awk, sed that can aid further development.  
Further, a better understanding of how end users will consume preserved software will help to shape how
software is preserved in the first place.
\end{itemize}
